A Data-Driven Framework for Neural Field Modelling

### 2010-11-16 ltx/first_order_framework/LaTeX_Manuscript.tex
edits from David to discussion

\section{Discussion}\label{DiscussionSection}
This paper has presented a framework for creating data-driven neural field models by deriving a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data. In doing so, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred. The mathematical formulation that we have presented scales well with the number of sensors, and we have derived a finite-order state-space representation that allows us to perform inference efficiently.

>>>>

\section{Discussion}\label{DiscussionSection}
This paper has presented a framework for creating data-driven neural field models by developing a method for estimating intracortical connectivity and synaptic dynamics from electrophysiological data. In doing so, we have highlighted important aspects of the experiment design process, demonstrating the relationship between sensor bandwidth and the complexity of the field that can be inferred. We have derived a finite-order state-space representation of the neural field equations that allows us to perform inference efficiently and the mathematical formulation that we have presented scales well with the number of sensors.
